Predicting the conformational preferences of proteins using a physics-based free energy method

### 2013-03-06 Paper/paper.tex

\Alberto{The last 50 years represent our effort to understand what the native state of a protein
    looks like by using theoretical methods. Experimental evidence coming from NMR and x-ray
    cristallography remain so far the only real ways to solve the structure of the native state.
    However, this methods are expensive and slow. Theoretical methods on the other hand are cheaper,
    but despite improvement still have a long way to go. Often this computational pipelines produce
    ensembles of diverse structures and identifying which structure is more native like is still a
    problem. Here we have shown how the application of the confinement method can help identify
    native like states. The high success rate balances with the computational expense. However, with
    GPU technology and the rate at which computers improve, this computational expense is becoming
less of a bottle neck.}
\Alberto{I don't agree with some of the points here, but I think I covered what you meant in the
previous paragraph}

@@

>>>>

The last 50 years represent our effort to understand what the native state of a protein
    looks like by using theoretical methods. Experimental evidence coming from NMR and x-ray
    cristallography remain so far the only real ways to solve the structure of the native state.
    However, this methods are expensive and slow. Theoretical methods on the other hand are cheaper,
    but despite improvement still have a long way to go. Often this computational pipelines produce
    ensembles of diverse structures and identifying which structure is more native like is still a
    problem. Here we have shown how the application of the confinement method can help identify
    native like states. The high success rate balances with the computational expense. However, with
    GPU technology and the rate at which computers improve, this computational expense is becoming

less of a bottle neck.

\Alberto{I don't agree with some of the points here, but I think I covered what you meant in the
previous paragraph}

@@

less of a bottle neck.
We foresee great potential for this methodology for two reasons: independence from a reaction
coordinate (just need start and end state) and avility to decompose the free energies on a per
residues basis. This last point can be very useful in protein design. Finally, we have presented
data for structure comparison of proteins, but we are currently exploring the possibility of
using this methodology for getting free energies of ligand-protein binding.

\Alberto{Do we mention this in the text? too technical for conclusions:
There is another issue, which is normal mode
analysis calculations are Oh(N**3) and require large amounts of memory, effectively limiting the
size of the systems under study. In most cases quasiharmonic analysis.
}
